The testing implementation was developed with high modularity in
mind, since it is meant to be a proof-of-concept implementation and
not a a production grade system. High modularity also makes
development easier and the system more robust against changes, two
very important qualities during this project.

The implementation consists of three main parts:
\begin{description}
  \item[Particle Filter] An implementation of the procedure in table \ref{alg:pf}.
  \item[Database] A database with functions for extracting transition
    hypotheses. Provides the prediction PDF $\cprobnext{x}$ to the
    particle filter.
  \item[Tracker] Manages the model and performs matching between
    hypotheses and images. Provides the filtering PDF
    $\cprob{I_n}{x_n}$ to the particle filter.
\end{description}

\section{The particle filter}
    A plug-n-play algorithm which only lacks the problem-domain<ref:encyc> specific parts:$x_0$, $\cprob{x_t}{x_{t-1}}$ and $\cprob{I_t}{x_t}$
    \subsection{Initilization $x_0$}
        The particle filter only does tracking thus we need to have an initial guess for $t=0$ which in our case will be hand labeled foreach whisker.
   ======

Since the algorithm only does tracking, we also need to initialize the algorithm with a start guess $x_0$. 
Using this we take a number of samples $X_0 \sim \ndist{x_0}{\Sigma}$ and let the set $X_0$ be an approximation 
of $\prob{Z_0}$. However, the problem of automatic initialization is a difficult one\cite{Hedvig}, and is not covered in this thesis. 
In the testing implementation, knowledge of the start state $Z_0$ is assumed, meaning $x_0 := Z_0$ and $\Sigma := 0$.
=====
    
    \subsection{Goodness $\kappa\cprob{x_t}{I_t}$}
        It also needs an direction to know how good the hypothesis $x_t$ matches the given image $I_t$.

        TODO <ref:theorem>
    \subsection{Sampling $\cprobnext{x}$}

        ...

\section{The state transition database}





\section{Real data}
    \subsection{Pre-processing}

    We want to find the function $\prob{I=\text{whisker}}\in\IS$

    >We want to have a measure on how probable it is for a pixel to hosehould a whisker





